---
title: "writing_functions"
author: "Xicheng Xie"
date: "2022-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(rvest)
library(purrr)
```

```{r}
set.seed(1)
```

# My first function
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

```

## let's have multiple outputs

```{r}
mean_and_sd = function(x){
  mean_x=mean(x)
  sd_x=sd(x)
  
  tibble(
    mean=mean_x,
    sd=sd_x
  )
}
```

## let's start with simulations
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```


## let's write a fucntion to get reviews
```{r}
read_page_reviews = function(url){
  dynamite_html = read_html(url)

  review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

  review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

  review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()%>% 
  str_subset("The media could not be loaded.", negate = TRUE) %>% 
  str_subset("^$", negate = TRUE)

  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  ) 
  
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```
## iteration_and_listcols

lets look at a list

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))

l[[3]]
```

## loops!
let's write a `for` loop

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

```{r}
output=vector("list",length = 4)

for (i in 1:4){
  output[[i]]=mean_and_sd(list_norms[[i]])
}
output
```

## can we map
```{r}
map(list_norms,mean_and_sd)
```

```{r}
map_dbl(list_norms,median)
map_df(list_norms,mean_and_sd)
```

## list columns ... 
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )

listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd))

```

## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

let's nest within weather stations
```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
```

### a little lm function
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

## a loop
map(weather_nest[["data"]],weather_lm)
```

Let’s use mutate to fit this model, and to store the result in the same dataframe.
```{r}
weather_nest<-
weather_nest %>% 
  mutate(
    models=map(data,weather_lm)
  )

weather_nest[[4]][[1]]
```

```{r}
weather_nest %>% 
  unnest(data)
```

## Revisiting Napoleon
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

napoleon_reviews<-
  tibble(
    page=1:5,
    page_url=str_c(url_base,page)
  ) %>% 
  mutate(
    reviews=map(page_url,read_page_reviews)
  ) %>% 
  select(-page_url)

napoleon_reviews %>% 
  unnest(reviews)
```

